### 2012-05-22 docs/makefiles/makefiles.tex
more...

Several files are created at build-time:
\begin{itemize}
\item {\tt probin.f90}

\item {\tt build\_info.f90}

\item {\tt network.f90} (only for the {\tt general\_null} network)
\end{itemize}

@@

\subsection{Parallel Builds}

{\tt BOXLIB\_USE\_MPI\_WRAPPERS}

>>>>

Several files are created at build-time:
\begin{itemize}
\item {\tt probin.f90}:

  This is the module that controls runtime parameters.  This is
  created by the script
  {\tt write\_probin.py} in {\tt \$\{BOXLIB\_HOME\}/Tools/F\_scripts/}.  The
  makefile logic for creating it is in {\tt GMaestro.mak}.  At compile
  time, the problem, main {\tt MAESTRO/}, and {\tt extern/}
  directories are searched for {\tt \_parameter} files.  These files
  are parsed and the {\tt probin.f90} file is output containing the 
  runtime parameters, their default values, and the logic for reading
  and interpreting the inputs file.

\item {\tt build\_info.f90}:

  This is a module that contains basic information about the build
  environment (compiler used, build machine, build directory, compiler
  flags, etc.).  This is created by the script {\tt make\_build\_info}
  in {\tt \$\{BOXLIB\_HOME\}/Tools/F\_scripts/} from {\tt
  GMaestro.mak} by passing in a number of makefile variables.  This is
  rewritten everytime the code is compiled.  The primary use of this
  module is writing out the {\tt job\_info} file in the plotfiles.

\item ({\tt network.f90}):

  This is generated at compile time {\em only} for the {\tt
  general\_null} network.  The {\tt general\_null} network allows the
  user to define a list of non-reacting species builds the {\tt
  network.f90} based on this list.  The makefile logic for building
  the {\tt network.f90} is in the {\tt GPackage.mak} in {\tt
  extern/networks/general\_null}.  The script {\tt write\_network.py}
  in that directory does the actual parsing of the species file and
  outputs the {\tt network.f90}.

@@

\subsection{Parallel (MPI) Builds}

When building with MPI, the build system needs to know about the location of the
MPI libraries.  If your local MPI has the {\tt mpif90} and {\tt mpicc} wrappers
installed and working, then \maestro\ can use these simply by setting the
environment variable:
\begin{verbatim}
BOXLIB_USE_MPI_WRAPPERS=1
\end{verbatim}
Otherwise, you will need to edit {\tt GMakeMPI.mak} and add a section
specific to your machine with the compiler and library location.  It
is best to simply copy an existing similar portion of the makefile and
adjust it to your system.  Most national supercomputing facilities are
already supported, and parallel builds on them should work out of the
box.
